Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-04-21 ATVA 2025/experiments.tex
final

\subsection{Comparison with other Verifiers?}

We voluntarily limited the comparison to $\alpha,\beta$-Crown because it is one of the most efficient verifier to date, which allowed us to consider a spectrum of parameters to understand $\alpha,\beta$-Crown scaling without too much clutter.

>>>>

\subsection{Comparison with other Verifiers}

We voluntarily limited the comparison so far to $\alpha,\beta$-Crown because it is one of the most efficient verifier to date, which allowed us to consider a spectrum of parameters to understand $\alpha,\beta$-Crown scaling without too much clutter.
